HMM Model development

### 2020-04-30 dev/hmm_model_devel.Rmd
First rate HMM version passing SBC

```{r setup}
library(rstan)
library(tidyverse)
devtools::load_all()
```

@@

>>>>

```{r setup}
library(rstan)
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())

options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

devtools::load_all()
```

@@

```{r}
adapt_delta <- 0.8

data <- hmm_simulator(10, 20, 2)

if(inherits(model, "stanmodel")) {
  fit <- sampling(model, data = data$observed, control = list(adapt_delta = adapt_delta))
} else {
  cmdstan_fit <- model$sample(data = data$observed, adapt_delta = adapt_delta)
  fit <- rstan::read_stan_csv(cmdstan_fit$output_files())
}
evaluation_summary(fit, data$true)

```

```{r}
sbc_res <- sbc(model, generator = function() {hmm_simulator(10, 20, 2) }, N_steps = 100, control = list(adapt_delta = adapt_delta))

saveRDS(sbc_res, "sbc.rds")

sbc_res$params %>% filter(grepl("rates", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("sensitivity", param_name)) %>% plot_sbc_params()
#sbc_res$params %>% filter(grepl("initial", param_name)) %>% plot_sbc_params()

#sbc_res$params %>% plot_sbc_params()
summarise_sbc_diagnostics(sbc_res)
sbc_res$diagnostics

```
